### 2021-02-14 treatise-context/1_introduction.tex
LaTeX chap 1 literature review
LaTeX: align equations

Here the constant \m {\d_s} in Definition [1] is significant, since we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite [BDD08] that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.

Back to our problem of MIMO channel estimation, recall that, luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
Bajwa et.\ al.\ \cite [BHS10] used DS, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
The accompanying note by the same researchers \cite [BHR08] showed that \m {X} has RIP for overwhelming probability, justifying their work.

Some scholars applied least absolute shrinkage and selection operator (Lasso) instead.
In fact, it can be shown that Lasso and DS have similar behavior \cite [AsR10].

Lian, Liu and Lau applied Lasso on MIMO with an analog combiner \cite [LLL17].
Destino, Juntti, and Nagaraj used an adaptive Lasso \cite [DJN15], in which they jointly optimize the sensing matrix and pilot vectors.
Vlachos, Alexandropoulos, and Thompson \cite [VAT19] used Lasso on hybrid beamforming with an additional random spatial sampling device.

@@

\Result
{Algorithm}
{
\startitemize[n]
%
\item Input \m {\M {Q} \in \MB {R} ^{N_m \D N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
%
\item Initialize
%
\Disp {
\NC \V {r}
\LA \NC \V {y} \NR
%
\NC S
\LA \NC \varnothing \NR
}
%
\item Start the loop with counter \m {i \LA 1}.
%
\item Find
%
\DispNum {n:n:n0:nr} {
\NC n
\LA \NC \underset {n' =0, \dots, N_p-1} {\Rm {argmax}}
\Nm {\M {Q} _{\SB {:,n'}} \V {r}} \NR
}
%
and append \m {S \LA S \cup {n}}.
%
\item Compute
%
\DispNum {Q:Q:QS:Qy} {
\NC \M {Q} ^\ddagger
\LA \NC \RB {\M {Q} _{\SB {S}} ^\Adj \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\Adj \NR
%
\NC \V {r}
\LA \NC \V {y} -\M {Q} _{\SB {S}} ^\Adj \M {Q} ^\ddagger \V {y} \NR
}
%
\item Break if
%
\DispNum {r:2:h':h'} {
\NC \VNm {\V {r}} _2
<\NC \eta \NR
}
%
otherwise, go to step 4.
%
\item Output 
%
\DispNum {g:g:Qy:Qy} {
\NC \Hat {\V {g}}
\LA \NC \M {Q} ^\ddagger \V {y} \NR
}
\stopitemize
}
%
The columns of \m {\M {Q}} are chosen greedily, and we expect its columns to span \m {\V {x}}, playing a role similar to the sensing matrix in the case of DS.
In each step, we estimate the noise \m {\V {r}}, and find a new column most correlated with it, to refine the estimation for \m {\V {x}}.
From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming.

>>>>

Here the constant \m {\d_s} is significant, since we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite [BDD08] that if \m {\VNm {\M {Q} \V {x}} _2} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.

Back to our problem of MIMO channel estimation, recall that, luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
Bajwa et.\ al.\ \cite {BHS10} used DS, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response,
and in the accompanying note \cite {BHR08} they justified that \m {X} has RIP for overwhelming probability.

Some scholars applied least absolute shrinkage and selection operator (Lasso) instead.
In fact, it can be shown that Lasso and DS have similar behavior \cite [AsR10].
Lian, Liu and Lau applied Lasso on MIMO with an analog combiner \cite [LLL17].
Destino, Juntti, and Nagaraj used an adaptive Lasso \cite [DJN15], in which they jointly optimize the sensing matrix and pilot vectors.
Vlachos, Alexandropoulos, and Thompson \cite [VAT19] used Lasso on hybrid beamforming with an additional random spatial sampling device.

@@

\Result
{Algorithm}
{
\startitemize[n]
%
\item Input \m {\M {Q} \in \MB {R} ^{N_m \D N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
%
\item Initialize
%
\Disp {
\NC \V {r}
\LA \NC \V {y} \NR
%
\NC S
\LA \NC \varnothing \NR
}
%
\item Start the loop with counter \m {i \LA 1}.
%
\item Find
%
\DispNum {n:n:n0:nr} {
\NC n
\LA \NC \underset {n' =0, \dots, N_p-1} {\Rm {argmax}}
\Nm {\M {Q} _{\SB {:,n'}} ^\Adj \V {r}} \NR
}
%
and append \m {S \LA S \cup {n}}.
%
\item Compute
%
\DispNum {Q:Q:QS:Qy} {
\NC \M {Q} ^\ddagger
\LA \NC \RB {\M {Q} _{\SB {S}} ^\Adj \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\Adj \NR
%
\NC \V {r}
\LA \NC \V {y} -\M {Q} _{\SB {S}} ^\Adj \M {Q} ^\ddagger \V {y} \NR
}
%
\item Break if
%
\DispNum {r:2:h':h'} {
\NC \VNm {\V {r}} _2
<\NC \eta \NR
}
%
otherwise, go to step 4.
%
\item Output 
%
\DispNum {g:g:Qy:Qy} {
\NC \Hat {\V {g}}
\LA \NC \M {Q} ^\ddagger \V {y} \NR
}
\stopitemize
}
%
The columns of \m {\M {Q}} are chosen greedily, and we expect its columns to span \m {\V {x}}, playing a role similar to the sensing matrix of DS.
In each step, we estimate the noise \m {\V {r}}, and find a new column most correlated with it, to refine the estimation for \m {\V {x}}.
It is shown that the probability that OMP recovers \m {\V {x}} completely is overwhelming \cite [TrG07a].

### 2021-02-14 treatise-context/2_problem_setting.tex
Transfer chap 1, 4 to LaTeX
check chap 2, 3 LaTeX
LaTeX: align equations

Recall that analog precoders may only have values of unity magnitude,
%
\DispNum {F:R:1::R1} {
\NC \Nm {\RB {\M {F} _R} _{\SB {n_H, n_R}}}
= \NC 1, \NR
%
\NC \Nm {\RB {\M {W} _R} _{\SB {n_R, n_H}}}
= \NC 1, \NR
%
\NC n_H
= \NC 0, \dots N_H-1, \NR
%
\NC n_{B,t}
= \NC 0, \dots N_{B,t}-1 \NR
%
\NC n_{B,r}
= \NC 0, \dots N_{B,r}-1 \NR
}
%
And we assume
%
\DispNum {N:H:NY:NY} {
\NC N_H \gg \NC N_{B,t}, N_{R,t} \NR
%
\NC N_{B,t}, N_{B,t} \NR
}

Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \MB {C} ^{N_{B,r} \D N_{B,t}}} with each entry being i.i.d.\ standard normal.
Let us introduce the effective channel
%
\DispNum {Y:Y:WB:BZ} {
\NC \M {Y}
:=\NC \M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} \NR
}
%
Our task then amounts to recovering \m {\M {H}}, and designing \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.

@@

It is more appealing to write
%
\DispNum {h:h:ve:Nh} {
\NC \V {h}
:= \NC \Rm {vec} \SB {\M {H}}
\in \MB {C} ^{N_H^2} \NR
%
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}}
\in \MB {C} ^{N_B^2} \NR
%
\NC \V {z}
:= \NC \Rm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
\in \MB {C} ^{N_B^2} \NR
%
\NC \M {Q}
:= \NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
\in \MB {C} ^{N_B^2 \D N_H^2} \NR
}
%
to formulate the problem as a linear system:
%
\DispNum {y:y:Qh:hz} {
\NC \V {y}
=\NC \M {Q} \V {h} +\V {z} \NR
}
%
At this stage, we intend to apply DS, but there is no guarantee that \m {\V {h}} must be sparse.

@@

Denote the discrete Fourier transform matrix to be \m {\M {K}},
%
\DispNum {K:K:CN:H1} {
\NC \M {K} \in  \NC \MB {C} ^{N_H \D N_H} \NR
%
\NC \M {K} _{\SB {n_1, n_2}}
= \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss {i} n_1 n_2 /N_H}, \NR
%
\NC \Q n_1, n_2
= \NC 0, 1, \dots, N_H-1 \NR
}
%
Recall that we have
%
\DispNum {K:K:I:::I} {
\NC \M {K}^\Adj \M {K}
= \NC \M {I} \NR
}
%
If we write
%
\DispNum {G:G:KH:HK} {
\NC \M {G}
=\NC \M {K}^\Adj \M {H} \M {K} \NR
}
%
then \m {\M {G}} can be interpreted as spatial frequency domain representation of \m {\M {H}}.
%
\DispNum {Y:Y:WB:NY} {
\NC \M {Y}
=\NC \M {W} _B \M {W} _R \M {K} \D \M {G} \D \M {K}^\Adj \M {F} _R \M {F} _B
+\M {W} _B \M {W} _R \M {Z}
\in \MB {C} ^{N_B \D N_B} \NR
}
%
If we are sure that \m {\M {G}} is sparse, then we recover \m {\M {G}} instead.
Set for brevity
%
\DispNum {P:P:FB:Nh} {
\NC \M {P}
:=\NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
\in \MB {C} ^{N_B^2 \D N_H^2} \NR
}
%
and
%
\DispNum {g:g:ve:Nh} {
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {G}}
\in \MB {C} ^ {N_H \D N_H} \NR
}
%
accordingly
%
\DispNum {y:y:Pg:gz} {
\NC \V {y}
=\NC \M {P} \V {g} +\V {z} \NR
}

>>>>

Recall that analog precoders may only have values of unity magnitude,
%
\DispNum {F:R:1::R1} {
\NC \Nm {\RB {\M {F} _R} _{\SB {n_H, n_{R,t}}}}
= \NC 1, \NR
%
\NC \Nm {\RB {\M {W} _R} _{\SB {n_{R,r}, n_H}}}
= \NC 1, \NR
%
\NC n_H
= \NC 0, \dots N_H-1, \NR
%
\NC n_{R,t}
= \NC 0, \dots N_{B,t}-1 \NR
%
\NC n_{R,r}
= \NC 0, \dots N_{B,r}-1 \NR
}
%
And we assume
%
\DispNum {N:H:NY:NY} {
\NC N_H \gg \NC N_{B,t}, N_{R,t} \NR
}

Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \MB {C} ^{N_H \D N_{B,t}}} with each entry being i.i.d.\ standard normal.
Let us introduce the effective channel
%
\DispNum {Y:Y:WB:BZ} {
\NC \M {Y}
:=\NC \M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} \NR
}
%
Our task then amounts to recovering \m {\M {H}}, and generating \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.

@@

It is more appealing to write
%
\DispNum {h:h:ve:Nh} {
\NC \V {h}
:= \NC \Rm {vec} \SB {\M {H}}
\in \MB {C} ^{N_H^2} \NR
%
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}}
\in \MB {C} ^{N_{B,t} N_{B,r}} \NR
%
\NC \V {z}
:= \NC \Rm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
\in \MB {C} ^{N_{B,t} N_{B,r}} \NR
%
\NC \M {Q}
:= \NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
\in \MB {C} ^{N_{B,t} N_{B,r} \D N_H^2} \NR
}
%
to formulate the problem as a linear system:
%
\DispNum {y:y:Qh:hz} {
\NC \V {y}
=\NC \M {Q} \V {h} +\V {z} \NR
}
%
At this stage, we intend to apply DS, but there is no guarantee that \m {\V {h}} must be sparse.

@@

Denote the discrete Fourier transform matrix to be \m {\M {K}},
%
\DispNum {K:K:CN:H1} {
\NC \M {K} \in  \NC \MB {C} ^{N_H \D N_H} \NR
%
\NC \M {K} _{\SB {n_1, n_2}}
= \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss {i} n_1 n_2 /N_H}, \NR
%
\NC \Q n_1, n_2
= \NC 0, 1, \dots, N_H-1 \NR
}
%
Recall that we have
%
\DispNum {K:K:I:::I} {
\NC \M {K}^\Adj \M {K}
= \NC \M {I} \NR
}
%
If we write
%
\DispNum {G:G:KH:HK} {
\NC \M {G}
=\NC \M {K}^\Adj \M {H} \M {K} \NR
}
%
then \m {\M {G}} can be interpreted as spatial frequency domain representation of \m {\M {H}}.
%
\DispNum {Y:Y:WB:NY} {
\NC \M {Y}
=\NC \M {W} _B \M {W} _R \M {K} \D \M {G} \D \M {K}^\Adj \M {F} _R \M {F} _B
+\M {W} _B \M {W} _R \M {Z}
\in \MB {C} ^{N_{B,r} \D N_{B,t}} \NR
}
%
If we are sure that \m {\M {G}} is sparse, then we recover \m {\M {G}} instead.
Set for brevity
%
\DispNum {P:P:FB:Nh} {
\NC \M {P}
:=\NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
\in \MB {C} ^{N_{B,t} N_{B,r} \D N_H^2} \NR
}
%
and
%
\DispNum {g:g:ve:Nh} {
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {G}}
\in \MB {C} ^ {N_H \D N_H} \NR
}
%
accordingly
%
\DispNum {y:y:Pg:gz} {
\NC \V {y}
=\NC \M {P} \V {g} +\V {z} \NR
}

### 2021-02-14 treatise-context/3_2_generating_beamforming_matrices.tex
LaTeX: align equations

\startsection [title={Generation of beamformers}]

\startsubsection [title={Generation of beamformers}]

We want to set the four beamformers to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.
Let us simply set each entry of \m {\M {F} _B} to be i.i.d.\ normal random variables with mean \m {0}, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
We know that the magnitude \m {\RB {\M {F} _B} _{\SB {n_R, n_B}}} follows Rayleigh distribution.
\m {\RB {\M {W} _B ^\Tr} _{\SB {n_B, n_R}}} is set similarly.
In addition, let \m {\RB {\M {F} _R} _{\SB {n_H, n_R}}} be uniformly distributed on the unit circle on the complex plane, multiplied by a normalizing constant \m {\l_R >0}.
\m {\RB {\M {W} _R ^\Tr} _{\SB {n_R, n_H}}} is set similarly.

@@

\startsubsection [title={Operator norm of digital beamformers}]

@@

\startsubsection [title={Operator norm of analog beamformers}]

>>>>

\startsection [title={Generating beamforming matrices}]

\startsubsection [title={The plan}]

We want to set the four beamforming matrices to be i.i.d.\ random matrix, hoping that the resulting \m {\M {P}} has RIP.
Let us simply set each entry of \m {\M {F} _B} to be i.i.d.\ normal random variables with mean \m {0}, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
We know that the magnitude \m {\RB {\M {F} _B} _{\SB {n_R, n_B}}} follows Rayleigh distribution.
\m {\RB {\M {W} _B ^\Tr} _{\SB {n_B, n_R}}} is set similarly.
In addition, let \m {\RB {\M {F} _R} _{\SB {n_H, n_R}}} be uniformly distributed on the unit circle on the complex plane, multiplied by a normalizing constant \m {\l_R >0}.
\m {\RB {\M {W} _R ^\Tr} _{\SB {n_R, n_H}}} is set similarly.

@@

\startsubsection [title={Operator norm of digital beamforming matrices}]

@@

\startsubsection [title={Operator norm of analog beamforming matrices}]

### 2021-02-14 treatise-pdflatex/1_introduction.tex
LaTeX: align equations

We introduce some conventions.
For \m {\mathcal {A} \subseteq \CB {0, \dots, N_p-1}}, denote
%
\Disp {
\V {x}  _{\SB {\mathcal {A}}}
=\sum _{i \in \mathcal {A}} \V {v} \V {u} _{i} \\
%
\M {Q}  _{\SB {\mathcal {A}}}
=\sum _{i \in \mathcal {A}} \M {Q} _{\SB {:,i}} 
}
%
That is, respectively, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\mathcal {A}}.

\Result
{Definition}
{
For fixed \m {s =0, \dots N_p -1}, we say that \m {\M {Q}} satisfies \m {\d_s}-restricted isometry property (hereafter \m {\d_s} RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if for all \m {s}-sparse \m {\V {x}}
%
\DispNum {1:2:Qx:22} {
\RB {1-\d_s} \VNm {\V {x}} _2 ^2
\leq \VNm {\M {Q} \V {x}} _2 ^2 \\
%
\leq \RB {1+\d_s} \VNm {\V {x}} _2 ^2 
}
}
%
It helps to think that \m {\M {Q}} is almost unitary up to relative error \m {\d_s}.

@@

Here the constant \m {\d_s} is significant, since we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite {BDD08} that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.

Back to our problem of MIMO channel estimation, recall that, luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
Bajwa et.\ al.\ \cite {BHS10} used DS, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
The accompanying note by the same researchers \cite {BHR08} showed that \m {X} has RIP for overwhelming probability, justifying their work.

@@

\Result
{Algorithm}
{
\begin {itemize}
%
\item Input \m {\M {Q} \in \mathbb {R} ^{N_m \D N_p}} and \m {\V {y} \in \mathbb {R} ^{N_m}}, \m {\eta >0}.
%
\item Initialize
%
\Disp {
\V {r}
\leftarrow \V {y} \\
%
S
\leftarrow \varnothing 
}
%
\item Start the loop with counter \m {i \leftarrow 1}.
%
\item Find
%
\DispNum {n:n:n0:nr} {
n
\leftarrow \underset {n' =0, \dots, N_p-1} {\mathrm {argmax}}
\Nm {\M {Q} _{\SB {:,n'}} \V {r}} 
}
%
and append \m {S \leftarrow S \cup {n}}.
%
\item Compute
%
\DispNum {Q:Q:QS:Qy} {
\M {Q} ^\ddagger
\leftarrow \RB {\M {Q} _{\SB {S}} ^\dagger \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\dagger \\
%
\V {r}
\leftarrow \V {y} -\M {Q} _{\SB {S}} ^\dagger \M {Q} ^\ddagger \V {y} 
}
%
\item Break if
%
\DispNum {r:2:h':h'} {
\VNm {\V {r}} _2
<\eta 
}
%
otherwise, go to step 4.
%
\item Output 
%
\DispNum {g:g:Qy:Qy} {
\hat {\V {g}}
\leftarrow \M {Q} ^\ddagger \V {y} 
}
\end {itemize}
}
%
The columns of \m {\M {Q}} are chosen greedily, and we expect its columns to span \m {\V {x}}, playing a role similar to the sensing matrix in the case of DS.
In each step, we estimate the noise \m {\V {r}}, and find a new column most correlated with it, to refine the estimation for \m {\V {x}}.
From Tropp and Gilbert \cite {TrG07a}, the probability that OMP recovers \m {\V {x}} completely is overwhelming.

@@

The literature on channel estimation favors OMP for its low complexity, but we wonder how greedy algorithms, such as OMP, compare to convex programs, such as DS.
It might be that greedy algorithms trade precision for complexity, and that the opposite is true of convex programs.

In this treatise, we consider a hybrid system with uniform linear array as in Lee, Gil, and Lee \cite {LGL16}.
They proposed a beamformer shown to be optimal, jointly designed on both ends by a nonconvex optimization program, and due to its difficulty they have made considerable approximation.
Is the approximated design still optimal, or are the angles of sensing matrix not sufficiently precise?

In chapter 2 we shall see that our proposed effective beamformer has RIP for high probability, which may serve as the sensing matrix for DS.
In chapter 3, along the lines of Candès and Tao \cite {CaT07}, we give a quantitative bound (which holds for high probability) on expected error norm.
In chapter 4, we remark that DS can be cast as a linear program, for which more efficient algorithms exist.
Numerical results show that in our problem configuration, DS is superior to other methods.
Indeed, DS is much more accurate than the least square, and both OMP and Lasso often fails.

>>>>

We introduce some conventions.
For \m {\mathcal {A} \subseteq \CB {0, \dots, N_p-1}}, denote
%
\Disp {
\V {x}  _{\SB {\mathcal {A}}}
=&\sum _{i \in \mathcal {A}} \V {v} \V {u} _{i} \\
%
\M {Q}  _{\SB {\mathcal {A}}}
=&\sum _{i \in \mathcal {A}} \M {Q} _{\SB {:,i}} 
}
%
That is, respectively, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\mathcal {A}}.

\Result
{Definition}
{
For fixed \m {s =0, \dots N_p -1}, we say that \m {\M {Q}} satisfies \m {\d_s}-restricted isometry property (hereafter \m {\d_s} RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if for all \m {s}-sparse \m {\V {x}}
%
\DispNum {1:2:Qx:22} {
\RB {1-\d_s} \VNm {\V {x}} _2 ^2
\leq &\VNm {\M {Q} \V {x}} _2 ^2 \notag \\
%
\leq &\RB {1+\d_s} \VNm {\V {x}} _2 ^2 
}
}
%
It helps to think that \m {\M {Q}} is almost unitary up to relative error \m {\d_s}.

@@

Here the constant \m {\d_s} is significant, since we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite {BDD08} that if \m {\VNm {\M {Q} \V {x}} _2} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.

Back to our problem of MIMO channel estimation, recall that, luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
Bajwa et.\ al.\ \cite {BHS10} used DS, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response,
and in the accompanying note \cite {BHR08} they justified that \m {X} has RIP for overwhelming probability.

@@

\Result
{Algorithm}
{
\begin {itemize}
%
\item Input \m {\M {Q} \in \mathbb {R} ^{N_m \D N_p}} and \m {\V {y} \in \mathbb {R} ^{N_m}}, \m {\eta >0}.
%
\item Initialize
%
\Disp {
\V {r}
\leftarrow &\V {y} \\
%
S
\leftarrow &\varnothing 
}
%
\item Start the loop with counter \m {i \leftarrow 1}.
%
\item Find
%
\DispNum {n:n:n0:nr} {
n
\leftarrow \underset {n' =0, \dots, N_p-1} {\mathrm {argmax}}
\Nm {\M {Q} _{\SB {:,n'}} ^\dagger \V {r}} 
}
%
and append \m {S \leftarrow S \cup {n}}.
%
\item Compute
%
\DispNum {Q:Q:QS:Qy} {
\M {Q} ^\ddagger
\leftarrow &\RB {\M {Q} _{\SB {S}} ^\dagger \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\dagger \\
%
\V {r}
\leftarrow &\V {y} -\M {Q} _{\SB {S}} ^\dagger \M {Q} ^\ddagger \V {y} 
}
%
\item Break if
%
\DispNum {r:2:h':h'} {
\VNm {\V {r}} _2
<\eta 
}
%
otherwise, go to step 4.
%
\item Output 
%
\DispNum {g:g:Qy:Qy} {
\hat {\V {g}}
\leftarrow \M {Q} ^\ddagger \V {y} 
}
\end {itemize}
}
%
The columns of \m {\M {Q}} are chosen greedily, and we expect its columns to span \m {\V {x}}, playing a role similar to the sensing matrix of DS.
In each step, we estimate the noise \m {\V {r}}, and find a new column most correlated with it, to refine the estimation for \m {\V {x}}.
It is shown that the probability that OMP recovers \m {\V {x}} completely is overwhelming \cite {TrG07a}.

@@

Due to the constraint of hybrid structure, the designs which use a fully digital beamforming cannot be directly applied, and the designs which use only analog beamforming might not be optimal.
Moreover, it appears possible that that convex programming outperforms greedy methods, and is necessary in less ideal situations.

In this treatise, we consider a hybrid structure with uniform linear array with both precoders and combiners on each side.
In chapter 2, we plan to generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
In chapter 3, we shall see that our proposed sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
and we give a quantitative bound (which holds for high probability) on expected error norm.
In chapter 4, numerical results show that DS is superior to other methods for our problem.
Considering its higher complexity, we remark that it can be cast as a linear program, and basis pursuit denoising form may be used.

It appears that, for given number of sampling, DS recovers more successfully than OMP.
Moreover, our setting is more general than Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} with only analog combiner,
and our random generation of sensing matrix is simpler than Lee, Gil, and Lee \cite {LGL16},
and we do not rely on additional assumption on sparsity as in Gao, Dai, and Wang \cite {GDW15}.

It also is different from Bajwa et.\ al.\ \cite {BHS10};
while they require a series of random pilot vectors and consequently the sensing stage take considerable time, we require only i.i.d.\ random sensing matrices and take just a few time frames.

In addition, it seems that with the same threshold, DS is better than Lasso.
Again, our proposed method is more general than Lian, Liu and Lau \cite {LLL17} with only analog combiner,
and our sensing matrix is generated more simply than in Destino, Juntti, and Nagaraj \cite {DJN15},
and we do not require special device as in Vlachos, Alexandropoulos, and Thompson \cite {VAT19}.
